\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-12 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added IBM Blue Gene compilation instructions for SCOTCH

\underline{More recent installation instruction for IBM BlueGene, from October 2012:}\\

@@

>>>>

\underline{More recent installation instruction for IBM BlueGene, from April 2013:}\\

@@

In order for the SCOTCH domain decomposer to compile, on some (but not all) Blue Gene systems after
running \texttt{configure} you may need to edit file src/decompose\_mesh/scotch/src/Makefile.inc and replace\\

\noindent
CCS    = bgxlc\_r \\
\noindent
CCD    = bgxlc\_r (or similar)\\

with:

\noindent
CCS    = gcc \\
\noindent
CCD    = gcc \\

and then type "make clean" and "make all".
